\documentclass[11pt]{article}
%Gummi|063|=)
\title{\textbf{Python Library: Image Processing}}
\author{}
\date{}
\usepackage{amsmath}
\usepackage{graphicx}
\begin{document}
\maketitle

\section{Goals}
We wanted to create a library that one could quickly and easily apply filters and effects to an image and chain these operations together. The setup of our library is that each function takes in a array of matrices representing r,g,b. A similar array is also returned from each function.

\section{Functions}
\begin{verbatim}
apply_transformation_matrix(array, transform, newSize=None)
\end{verbatim}
Applies a transformation matrix to the image.
\begin{verbatim}
gaussiangBlur(array, kernelSize=5, sigma=0.84089642)
\end{verbatim}
Applies Gaussian blur to the the image. sigma is the standard deviation of the curve. KernelSize is the size of points to sample around.
\begin{verbatim}
sobelEdgeDetection(array)
\end{verbatim}
Returns a grayscale representing edges. Edge detection uses the sobel operator.
\begin{verbatim}
flip(image, d)
\end{verbatim}
Flips a image around a direction specified by d. If d is 1, it flips vertically. If d is 2 it flips horizontally.
CHECK ME

\begin{verbatim}
greyscale(array)
\end{verbatim}
Converts the image into a gray scale. 
\begin{verbatim}
invert(array)
\end{verbatim}
Inverts each color channel in the image. 

\begin{verbatim}
load_image(imagefilepath)
\end{verbatim}

Load image into a array of r,g,b matrices. 

\begin{verbatim}
save_image(array, filename)
\end{verbatim}

Saves the image array into the specified file name.

\begin{verbatim}
color_balance(array,channel,num)
\end{verbatim}
Channel is 'red', 'green', 'blue', or 'all' and num is the amount to add to that channel.




\end{document}